---
output: 
  github_document: default
  html_document: default
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# generatr

This package is an attempt at an implementation of a "Pythonesque" generator data type and methods. It didn't work out 100% ... there's no magic `yield` method :( ... but I figured I'd share it anyways, in case anyone might find it useful.

See [here](https://wiki.python.org/moin/Generators) for more information on Python generators.

## Installation

Install from github with:
```{r eval = FALSE}
# install.packages("devtools")
devtools::install_github("ChrisMuir/generatr")
```

## Example Usage

```{r}
library(generatr)
```

Initialize a new `generator` object with an R vector
```{r}
gen <- gen_init_with_vector(c(1L, 5L, 20L, 45L))
```

Check the class of the object `gen`
```{r}
class(gen)
```

Use `gen_next()` to get the next value from a `generator` object, similar to Python's `__next__()`
```{r}
for (i in 1:4) {
  print(gen_next(gen))
}
```

Use `gen_current()` to get the current value from a `generator` object
```{r}
gen_current(gen)
```

Once all values have been exhausted, `gen_next()` will throw a `StopIteration` error
```{r error=TRUE}
gen_next(gen)
```

We can also initialize a new `generator` object as an empty object
```{r}
gen <- gen_init_empty(gen_type = "integer")
```

Again, check the class of object `gen`
```{r}
class(gen)
```

New items can be added one by one
```{r}
for (i in c(1L, 5L, 20L, 45L)) {
  gen_add_element(gen, i)
}
```

Once we're finished adding items, `gen_next()` and `gen_current()` work just like they did in the previous example
```{r}
for (i in 1:4) {
  print(gen_next(gen))
}
```

Currently, the only data types supported are `integer`, `numeric`, `character`, and `logical`
```{r}
gen <- gen_init_with_vector(c("cats", "dogs", "ducks", "frogs", "owls"))
for (i in 1:5) {
  print(gen_next(gen))
}
```
